### 2019-11-22 thesis/txt/3-data-set.tex
incorporate feedback about study / results section
try stuff on plots, add to discussion a bit

\paragraph{Build Sampling}
The \texttt{LogCollector} uses the \texttt{TravisRequester} to obtain the newest builds for a given repository.
Wwe use a stratified sampling approach: \texttt{TravisRequester} saves the obtained builds in buckets according to their status.
We encountered the following statuses during our data collection:
\begin{itemize}
	\item created
	\item started
	\item cancelled
	\item passed
	\item errored
	\item failed
\end{itemize}
The user of \texttt{TravisRequester} configures how many builds should be checked and how many builds per status should be saved.

@@

>>>>

\paragraph{Build Sampling}
The \texttt{LogCollector} uses the \texttt{TravisRequester} to obtain the newest builds for a given repository.
Wwe use a stratified sampling approach: \texttt{TravisRequester} saves the obtained builds in buckets according to their status.
We encountered the following statuses during our data collection:
\begin{multicols}{3}
\begin{itemize}
	\item created
	\item started
	\item cancelled
	\item passed
	\item errored
	\item failed
\end{itemize}
\end{multicols}
The user of \texttt{TravisRequester} configures how many builds should be checked and how many builds per status should be saved.

@@

\begin{figure}[htbp]
	\centering
	\includegraphics[width=\textwidth, clip]{img/big-study/categories-dataset.pdf}
	\caption{Distribution of the categories in LogChunks}
	\label{fig:categorycount-examplecount-dataset}
\end{figure}

### 2019-11-22 thesis/txt/5-study.tex
try stuff on plots, add to discussion a bit

\begin{figure}[htbp]
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/failure-reason-PBE.pdf}
		\caption{Results of chunk retrieval with PBE}
		\label{fig:failure-reason-PBE}
\end{figure}

@@

\begin{figure}[htbp]
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-examplecount-KWS.pdf}
		\caption{Precision and recall of chunk retrieval with KWS for increasing training set size}
		\label{fig:recall-precision-examplecount-KWS}
\end{figure}

\begin{figure}[htbp]
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-categorycount-KWS.pdf}
		\caption{Precision and recall of chunk retrieval with KWS for increasing number of structural categories in the training set}
		\label{fig:recall-precision-categorycount-KWS}
\end{figure}

\begin{figure}[htbp]
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/contextsizefactor-precision-recall-KWS.pdf}
		\caption{Precision and recall of chunk retrieval with KWS compared to retrieval size factor}
		\label{fig:contextsizefactor-precision-recall-KWS}
\end{figure}

\begin{figure}[htbp]
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/retrievalsizefactor-retrievalratio-KWS.pdf}
		\caption{Ratio of lines retrieved with KWS compared to retrieval size factor}
		\label{fig:retrievalsizefactor-retrievalratio-KWS}
\end{figure}

>>>>

\begin{figure}[htbp]
		\centering
		\includegraphics[width=0.75\textwidth, clip]{img/big-study/failure-reason-PBE.pdf}
		\caption{Results of chunk retrieval with PBE}
		\label{fig:failure-reason-PBE}
\end{figure}

@@

\begin{figure}[htbp]
		\centering
		\includegraphics[width=0.75\textwidth, clip]{img/big-study/recall-precision-examplecount-KWS.pdf}
		\caption{Precision and recall of chunk retrieval with KWS for increasing training set size}
		\label{fig:recall-precision-examplecount-KWS}
\end{figure}

\begin{figure}[htbp]
		\centering
		\includegraphics[width=0.75\textwidth, clip]{img/big-study/recall-precision-categorycount-KWS.pdf}
		\caption{Precision and recall of chunk retrieval with KWS for increasing number of structural categories in the training set}
		\label{fig:recall-precision-categorycount-KWS}
\end{figure}

\begin{figure}[htbp]
		\centering
		\includegraphics[width=0.75\textwidth, clip]{img/big-study/contextsizefactor-precision-recall-KWS.pdf}
		\caption{Precision and recall of chunk retrieval with KWS compared to retrieval size factor}
		\label{fig:contextsizefactor-precision-recall-KWS}
\end{figure}

\begin{figure}[htbp]
		\centering
		\includegraphics[width=0.75\textwidth, clip]{img/big-study/retrievalsizefactor-retrievalratio-KWS.pdf}
		\caption{Ratio of lines retrieved with KWS compared to retrieval size factor}
		\label{fig:retrievalsizefactor-retrievalratio-KWS}
\end{figure}

### 2019-11-22 thesis/txt/6-discussion.tex
try stuff on plots, add to discussion a bit

\begin{table}[htbp]
\begin{tabular}{|c||c|c|c|}
  Technique & \multicolumn{3}{|c|}{Number of Categories in configuring examples} \\
  \hline
  & one & two & more \\
  PBE & yes & no & no \\ 
  CTS & yes & yes & no \\ 
  KWS & yes & yes & yes \\ 
  \hline
\end{tabular}
\caption{The small $1 \cdot 1$}
\label{tab:101}
\end{table}

>>>>

\begin{table}[htbp]
\begin{tabular}{|c||c|c|c|}
  & PBE & CTS & KWS \\
  \hline
  \hline
  Structural Categories & 1 & best if 1 & no influence \\
  Training Set Size & 1 - 3 & no influence & > 2 \\ 
  Precision & high (if synthesis succeeds) & medium & low \\ 
  Recall & high (if synthesis succeeds) & medium & high \\ 
  Confidence in Output Correctness & high & low & low (precision), high (recall) \\ 
  Output Consumption by & program & human & human \\ 
  \hline
\end{tabular}
\caption{Recommendations for each of the investigated chunk retrieval techniques}
\label{tab:101}
\end{table}

\begin{figure}[htbp]
		\centering
		\includegraphics[width=0.75\textwidth, clip]{img/crt-recommendation.pdf}
		\caption{Our preliminary recommendation scheme for chunk retrieval techniques}
		\label{fig:fcrt-recommendation}
\end{figure}
